Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2017-04-27 Ben_Manuscripts/Paper1/methods.tex
more text writtenx

Each pore consists of twenty stacked monomer layers with periodic 
continuity in all directions, avoiding any edge effects and creating an
infinite length pore ideal for studying transport
(Fig.~\ref{fig:initial}). A small number of layers is preferred in order
to reduce computational cost and to allow us look at longer timescales.
Ultimately, we chose to build a system with 20 layers of monomer in each
pore in order to give sufficient resolution when simulating X-ray 
diffraction patterns.

% Questionably needed figure
\begin{figure}
\includegraphics{placeholder.png}
	\caption{Monomers are placed in an initial configuration close to
	         the expected equilibrium configuration and allowed to relax}
	\label{fig:initial}
\end{figure}

@@

An equilibration scheme with position restraints placed on benzene rings
prevents unrealistic jumps during early equilibration steps. Restraints
allow the system to remain in the sandwiched and parallel-displaced 
configurations while monomer tails settle. Doing so also helps prevent
system dependence on initial monomer configuration. During the restrained
equilibration, force constants are reduced by the square root of the 
previous force constant, with a starting value of 1e6.  by the
\begin{itemize}
	\item Equilibration scheme:
	\begin{itemize}
		\item Apply position restraints to monomer head groups during energy minimization 
		\item Leave position restraints on for nvt simulations to allow tails to intermingle (this also helps ensure independence of starting configuration)
		\item Gradually reduce force constants from 1000000 (by square root every 50 ps) until they are completely off
		\item Run long NPT simulations at 300 K and 1 bar ( $>$200 ns ) to fully equilibrate 
	\end{itemize}
\end{itemize}

Using an equilibrated structure, a crosslinking procedure was performed in order to better parallel synthetic procedures. 
\begin{itemize}
	\item Crosslinking maintains alignment of cylindrical mesophases - emphasize that replicating the mechanism/kinetics is not important 
	\item head to tail addition dominates so I only implemented that
	\item racemic mixture - don't have to be too concerned about direction of attack 
	\item Details of crosslinking algorithm (refer to appendix or supplemental info but give a brief overview here)
\end{itemize}

Simulated X-ray diffraction patterns were generated based on atomic coordinates to give a deeper understanding of the pore structure and spacing. 
\begin{itemize}
	\item 3 dimensional fourier transformed electron density generates simulated 1D and 2D diffraction patterns
        \item The 1D patterns are generated by spherical integration of the FT
        \item 2D patterns are generated by taking cross sections of the FT in the qx, qy and qz planes
        \item We matched experiments based on iterative improvement of our choice in initial structure and equilibration procedure
\end{itemize}

>>>>

Each pore consists of twenty stacked monomer layers with periodic 
continuity in all directions, avoiding any edge effects and creating an
infinite length pore ideal for studying transport. A small number of
layers is preferred in order to reduce computational cost and to allow
us look at longer timescales. Ultimately, we chose to build a system
with 20 layers of monomer in each pore in order to give sufficient
resolution when simulating X-ray diffraction patterns.

% Questionably needed figure
%\begin{figure}
%\includegraphics{placeholder.png}
%	\caption{Monomers are placed in an initial configuration close to
%	         the expected equilibrium configuration and allowed to relax}
%	\label{fig:initial}
%\end{figure}

@@

An equilibration scheme with position restraints placed on benzene rings
prevents unrealistic jumps during early equilibration steps. Restraints
allow the system to remain in the sandwiched and parallel-displaced 
configurations while monomer tails settle. Doing so also helps prevent
system dependence on initial monomer configuration. During the restrained
equilibration, force constants are reduced by the square root of the 
previous force constant every 50 ps, with a starting value of 1e6 kJ
mol\textsuperscript{-1} nm\textsuperscript{-2}. Once the force constant
is below 10 KJ mol\textsuperscript{-1} nm\textsuperscript{-2}, the 
restraints are slowly released until there is no more restriaining 
potential. All restrained equilibrations are run in the NVT ensemeble. 
The resulting unrestrained structure is subsequently allowed to 
equilibrate in the NPT ensemble for > 200 ns.

Determination of equilibration 
\begin{itemize}
	\item Pore spacing 
	\item Benzene ring stacking
	\item

Using an equilibrated structure, a crosslinking procedure was performed
in order to better parallel synthetic procedures. The purpose of 
crosslinking is to maintain macroscopic alignment of the crystalline
domains, ensuring aligned, hexagonally packed pores. For that reason, we
are not concerned with replicating the kinetics of the reaction, but
instead emphasize the consistency of the final structure with experimental
structural data. The algorithm was developed based on the known reaction
mechanism. Crosslinking of this system is a free radical polymerization (FRP)
taking place between terminal alkyl groups present on each of the three
monomer tails. FRPs require an initiator which bonds to the system, 
meaning new atoms were introduced into the system. For simplicity, the 
initiator was simulated as hydrogen and made present in the simulation
by including them in all possible bonding positions as dummy atoms.
The crosslinking procedure is carried out iteratively. During each 
iteration, bonding carbon atoms are chosen based on a distance cut-off.
The topology is updated with new bonds and dummy hydrogen atoms are 
changed to appropriate hydrogen types. Head-to-tail addition was the
only propagation mode considered due to its dominance in real systems.
Direction of attack was not considered because the resultant mixture is
racemic. The resulting crosslinked structure has an even distribution of
crosslinks between monomer tails of the same monomer, monomers stacked on
top of each other and monomers in other pores, including across periodic
boundaries. The pore spacing shrinks by $\approx$ 1 nm and stays 
constant under a range of simulation conditions (see supplemental info).

Simulated X-ray diffraction patterns were generated based on atomic
coordinates to give a deeper understanding of the pore structure and
spacing. All atomic coordinates were simulated as gaussian spheres of
electron density  corresponding to each atom's atomic number. A three
dimensional fourier transform (FT) of the array of electron density 
results in a 3 dimensional representation of the unit cell in reciprocal
space. Cross sections of the 3D FFT result in two dimensional reciprocal
space patterns which represent 2D diffraction patterns. Spherical
integration of the FT yields a 1 dimensional curve which is the same
as that generated in a diffraction experiment. We matched experimental
1D and 2D WAXS patterns by iterative improvement of our choice of 
initial structure and equilibration procedure
